Optimal coordination - general experiment analysis.

### 2019-06-20 voltagebudget/analysis/optimal_analysis.Rmd
Tweak  general opt. analysis notebook

```{r, message=FALSE}
# Data
algs <- c("max", "left", "uni", "cc")
alg_names <- c("max", "left", "uniform", "coincidence")
exps <- c(82, 83, 84, 85)

@@

>>>>

```{r, message=FALSE}
# Data
algs <- c("max", "left", "uni", "cc")
alg_names <- c("max", "left", "uniform", "coincidence")
# exps <- c(82, 83, 84, 85)
exps <- c(120, 121, 122, 123)

@@

```{r, fig.width=1.4, fig.height=0.8}
results %>% 
  filter(alg != "left") %>%
  ggplot(aes(x=errors*1e3, y=obs_variances*1e3, color=alg)) +
  geom_point(size=0.6, alpha=0.9) +
  # scale_linetype_manual(values=c("longdash", "solid", "dotdash", "dot"), name="Algorithm") +
  theme_classic() +
  labs(x="Error (ms)", y="Variance (ms)")
```
